Calibration tests beyond classification

### 2021-03-17 paper/main.tex
Updates for camera-ready version (#1)

%\subsubsection*{Acknowledgments}
%
%Use unnumbered third level headings for the acknowledgments. All
%acknowledgments, including those to funding agencies, go at the end of the paper.

>>>>

\subsubsection*{Acknowledgments}

We thank the reviewers for all the constructive feedback on our paper.
This research is financially supported by the Swedish Research Council via the
projects \emph{Learning of Large-Scale Probabilistic Dynamical Models} (contract
number: 2016-04278), \emph{Counterfactual Prediction Methods for Heterogeneous
Populations} (contract number: 2018-05040), and
\emph{Handling Uncertainty in Machine Learning Systems} (contract number: 2020-04122),
by the Swedish Foundation for Strategic Research via the project
\emph{Probabilistic Modeling and Inference for Machine Learning} (contract number: ICA16-0015),
by the Wallenberg AI, Autonomous Systems and Software Program (WASP) funded by the Knut and Alice
Wallenberg Foundation, and by ELLIIT.
